\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-12-03 resubmit_mnras/response.txt

This is confusing language. Fig 13 list the dashed line as "whitened". It is true though that the dotted curve gives the correct PSF for your matched filter, since it's the one that corresponds to the pre-filtered beam. The matched filter in Fourier space is B(k)N^-1(k), where the N^-1(k) is your pre-whitening step (dividing by the power spectrum of the noise). The B(k) is the PSF before the whitening. It seems like you say this here, but it's a bit confusing with the figure labeling. Maybe it would be useful to include a simple equation like  \Phi(k) =  B(k)N^-1(k) or similar to describe your total operation?

- Yes, we are essentially breaking down the typical B(k)/N^-1(k)
  matched-filter expression into two steps. We've clarified the text
  here.

+ Sec 4.3, Para 2: "Much like the reduction of a point source without any prior constraints (Fig 10c), degeneracies on scales larger than the array footprint and filter produce ripples in the map."

This sentence confused me. In the source case you had two things: 1) degeneracies between your map and the common mode that introduced very large modes, which you eliminated by wiping out those scales with a filter before estimating the map. And then you found 2) that the filter was ringing and producing ripples in the map. I think you're saying you have these two problems here but the sentence, as written, made it seem like the two were somehow interacting or somehow the same thing. Maybe something more explicit like "Much like…, mapping extended emission would suffer from degeneracy between the common mode and map (if no filter were used) and, once the filter is introduced, ringing around sources.

- Yes, this is confusing because we're mixing two ideas. In fact, both
  the high-pass filtering and the common-mode removal can have similar
  problems with degeneracies, but it depends on the scale of the
  filter relative to the array footprint. Some new text in both
  Section 4.1 and 4.3 now explains this better.

+ Sec 4.3, Para 4: "By the final iteration, most of the obvious structures in the data are encompassed by the mask…"

This is opposite the bright source case (example 1) in which everything but the source was masked. Since you're drawing an analogy (see previous comment) with the point source reduction, would you add a bit more description to explain why you use the "opposite" mask here?

- Our description was very confusing here! Due to a poor word choice
  it sounds as though we were using the inverse of what we really
  do. The portion of the map contrained to zero is where the SNR is
  *below* some threshold (so similar to the case of Uranus). This has
  been clarified.

+ Fig 18

Why is the jackknife noise higher than the map noise at small (<25") angular scales?

- Another careless mistake. The average maps used variance weighting,
  whereas the jackknife (difference) maps did not, leading to greater
  noise. This has now been fixed and the plots look more sensible at
  small scales.

+ Sec 4.3, Para 5: "at least a cosmetic sense"

in a cosmetic sense?

- Fixed.

+ Sec 4.3, Para 9: "in which the SNR threshold of 5 is again used to constrain the map"

A bit confusing, esp. b/c I only found S/N=5  mentioned before in a caption. Maybe "S/N threshold is used to define the extended brightness mask and constrain the map" or something a little more explicit like this...?

- Extra text added to clarify that pixels below this threshold are set to zero.

+ Sec 4.3, Para 13 "In this case the noise… in the left panel of the third row"

Would really help to give figure numbers here.

- Added.

+ Sec 4.3, Final Paragraph: "such structures have a chance to grow"

too vague -- "such structures" could be interpreted as the large scale astro structure. Maybe something like "degeneracies with the common mode have the chance to show up in the map"

- Text changed to something resembling this suggestion
